### 2022-09-20 main/chapter_context.tex
add sec references
add atlas cutaway figure

\subsection{Inner tracker}
\label{sec:atlas_tracker}
\TODO{inner tracker}
\begin{displayquote}
``%
The inner tracking detector covers the pseudorapidity range $|\eta| < 2.5$.
It consists of silicon pixel, silicon microstrip, and transition radiation
tracking detectors.
An additional layer of silicon pixels, the insertable
B-layer~\cite{ATLAS-TDR-19, PIX-2018-001}, was installed before Run~2.%
''~\cite{atlas2022searches}
\end{displayquote}

@@

\subsection{Trigger}
\label{sec:atlas_trigger}
% L1 L2 HLT
\TODO{trigger}
\begin{displayquote}
``%
A two-level trigger system is used to select events.
The first-level trigger is implemented in hardware and uses a subset of the
detector information to accept events at a rate below $100\,\mathrm{kHz}$.
This is followed by a software-based trigger that reduces the accepted event
rate to $1\,\mathrm{kHz}$ on average depending on the data-taking conditions.%
''~\cite{atlas2022searches}
\end{displayquote}

\subsection{Software}
\label{sec:atlas_software}
% how do we predict data?
\TODO{software and data?}
\begin{displayquote}
``%
An extensive software suite~\cite{ATL-SOFT-PUB-2021-001} is used in the
reconstruction and analysis of real and simulated data, in detector operations,
and in the trigger and data acquisition systems of the experiment.%
''~\cite{atlas2022searches}
\end{displayquote}

\subsection{Data}
\label{sec:atlas_data}
% discuss collisions, pileup, met, metsig

% LHC runs

>>>>

Figure~\ref{fig:atlas_cutaway}.

Inner detector~\ref{sec:atlas_inner}

Calorimeter systems~\ref{sec:atlas_calo}

Muon chambers~\ref{sec:atlas_muon}

Trigger~\ref{sec:atlas_trigger}

Software and data~\ref{sec:atlas_software_data}

\begin{figure}[tp]
\centering
\includegraphics[width=0.6\textwidth]{figures/atlas_cutaway_volume_1.pdf}
\caption[
A slice of \atlas' design
]{%
A slice of \atlas' design, reproduced from~\cite{atlas1999design1},
including a simulated event that interacts with several sensitive subsystems.
}
\label{fig:atlas_cutaway}
\end{figure}

\subsection{Inner detector}
\label{sec:atlas_inner}
\TODO{inner detector}
\begin{displayquote}
``%
The inner tracking detector covers the pseudorapidity range $|\eta| < 2.5$.
It consists of silicon pixel, silicon microstrip, and transition radiation
tracking detectors.
An additional layer of silicon pixels, the insertable
B-layer~\cite{ATLAS-TDR-19, PIX-2018-001}, was installed before Run~2.%
''~\cite{atlas2022searches}
\end{displayquote}

@@

\subsection{Trigger}
\label{sec:atlas_trigger}
\TODO{L1 HLT (L2, event thing)}
\TODO{trigger}
\begin{displayquote}
``%
A two-level trigger system is used to select events.
The first-level trigger is implemented in hardware and uses a subset of the
detector information to accept events at a rate below $100\,\mathrm{kHz}$.
This is followed by a software-based trigger that reduces the accepted event
rate to $1\,\mathrm{kHz}$ on average depending on the data-taking conditions.%
''~\cite{atlas2022searches}
\end{displayquote}

\subsection{Software and data}
\label{sec:atlas_software_data}
\TODO{how do we predict data?}
\TODO{software and data}
\begin{displayquote}
``%
An extensive software suite~\cite{ATL-SOFT-PUB-2021-001} is used in the
reconstruction and analysis of real and simulated data, in detector operations,
and in the trigger and data acquisition systems of the experiment.%
''~\cite{atlas2022searches}
\end{displayquote}

\TODO{discuss collisions, pileup, met}

\TODO{LHC runs}
